Should I Airbnb My Property: Analytic Code Explanation

### 2017-03-09 abbDataAnalysis_Script.Rmd
moving analyses from Writeup

## Global Market Analysis

We now analyze the full metro market to test which properties are more profitable as short-term rentals.

We start by specifying the imputation models for the LTR and the Airbnb datasets

@@

<!-- We then employ a custom function to cross impute rates and rents for the two datasets.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.  -->

<!--   imp.data <- imputeLtrRents(ltr.df=ltr.data,  -->
<!--                                str.df=str.data,  -->
<!--                                mod.spec=ltr.mod.spec, -->
<!--                                match.factor='suburb') -->

<!-- From the imputed results, we extract the base data (with imputed values) as well as the model summaries.  -->

<!--   # Extract out DFs (only those that imputed) -->
<!--   str.glob <- merge(str.data, imp.data$imp.rent, by='property.id') -->

<!-- Next we cross impute days on market and occupancy rates. -->

<!--   # Apply dom to abb -->
<!--   str.glob$imp.dom <- imputeDOM(str.glob, ltr.data, calc.type='median') -->

<!-- With the cross-imputed DOMs and occupancy rates we now make the cross-tenure imputations of revenues and add them back to the original datasets.  -->

<!--   str.glob$ltr.imp.revenue <- str.glob$imp.rent * (52 - str.glob$imp.dom / 7) -->

<!-- Next, we compare the revenues from the two and extract the new datasets. -->

<!--   comp.revs <- compareRevenues(str.glob) -->

<!--   str.glob <- merge(str.glob, comp.revs, by='property.id') -->

Realizing that the imputed long term rental values may be more accurate when estimated at smaller scales, we functionalize the above processes and then apply it to short term rentals, broken into submarkets by type, bed/bath and geographic area.  In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc. for all compbinations of type, bed/bath and geographic area. We then combine the results form all estimates back into a single data.frame that contains all of the short-term rentals.

@@

 str.data$tbg <- paste0(str.data$product,'.', str.data$sub.mrkt)
 ltr.data$tbg <- paste0(ltr.data$product,'.', ltr.data$sub.mrkt)

@@

  buildRevDensPlot(str.data.ic,
                   rev.cols=c(ltr.col, abb.col[2], str.col))

@@

## Analyze Results

First we make a comparison table of the results, broken down by submarket.

 # Make Basic comparison table
  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                   split.field='sub.mrkt')

 # Limit to the extrapolated pref type
  pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ]

@@

We then turn this into a simple chart to see the differences

  ggplot(pref.table, aes(x=ID, weights=Var, fill=ID)) + 
    geom_bar() +
    facet_grid(~rev.type) +
    scale_fill_manual(values=sm.col) +
    xlab('') +
    ylab('% of properties where Airbnb is more profitable') +
    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none')

Next, we plot the \% of properties that have short-term preference versus the occupancy rate

@@

  str.data.ic$pref <- str.data.ic$str.ext.pref

@@

@@

Next we build a heat map that shows which combinations of occ rate and nightly rate are most likely to result in short-term preference.

@@

  rate.hm <- abbHeatMap(str.data.ic,
                x.field='occ.rate',
                y.field='med.rate',
                pref.field='str.ext.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm

@@

  rate.hm.svm <- abbHeatMap(str.data.ic,
                            x.field='occ.rate',
                            y.field='med.rate',
                            pref.field='str.ext.pref',
                            svm=T, 
                            alpha.count=F,
                            add.points=T,
                            fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm.svm

@@

  qtl.hm <- abbHeatMap(str.data.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.ext.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm

@@

@@

  qtl.hm.svm <- abbHeatMap(str.data.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm.svm

@@

@@

  svm.rate <- makeSVM(str.data.ic,
                     x.field='occ.rate',
                     y.field='nightly.rate',
                     z.field='str.act.pref',
                     svm.type='C-svc',
                     svm.kernel='polydot',
                     poly.degree=4,
                     expand.factor=100)

  svm.qtl <- makeSVM(str.data.ic,
                      x.field='occ.qtl',
                      y.field='rate.qtl',
                      z.field='str.act.pref',
                      svm.type='C-svc',
                      svm.kernel='polydot',
                      poly.degree=4,
                      expand.factor=100)

  market.ratio <- data.frame(type=c('rate', 'qtl'),
                             actual=rep(mean(str.data.ic$str.act.pref), 2),
                             fitted=c(mean(svm.rate$orig$fitted),
                                      mean(svm.qtl$orig$fitted)),
                             svm=c(mean(svm.rate$pred$pred),
                                   mean(svm.qtl$pred$pred)))
```

@@

  mod.ext.str <- glm(str.ext.pref~type+as.factor(bedbath),
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.str <- glm(str.pot.pref~type+as.factor(bedbath),
                     family=binomial(link='logit'),
                     data=str.data.ic)
```

@@

  mod.ext.loc <- glm(str.ext.pref~type+as.factor(bedbath)+
                                  sub.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.loc <- glm(str.pot.pref~type+as.factor(bedbath)+
                                  sub.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
```

@@

  mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)

  pref.models <- list(mod.ext.str, mod.ext.loc, mod.ext.host, 
                      mod.pot.str, mod.pot.loc, mod.pot.host)
  names(pref.models) <- c('ext.str', 'ext.loc', 'ext.host',
                          'pot.str', 'pot.loc', 'pot.host')

@@

@@

  mod.ext.str.prem <- lm(str.ext.prem~type+as.factor(bedbath),
                    data=str.data.ic)
  mod.pot.str.prem <- lm(str.pot.prem~type+as.factor(bedbath),
                    data=str.data.ic)

  mod.ext.loc.prem <- glm(str.ext.pref~type+as.factor(bedbath)+
                                  sub.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.loc.prem <- glm(str.pot.pref~type+as.factor(bedbath)+
                                  sub.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)

@@

  mod.ext.host.prem <- lm(str.ext.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
  mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)

    prem.models <- list(mod.ext.str.prem, mod.ext.loc.prem, mod.ext.host.prem, 
                      mod.pot.str.prem, mod.pot.loc.prem, mod.pot.host.prem)
    names(prem.models) <- c('ext.str', 'ext.loc', 'ext.host',
                          'pot.str', 'pot.loc', 'pot.host')

@@

### Sensitivity

>>>>

Before we examine the distributions of the observed short-term revenues and the estimated long-term revenues, we must produce the estimates of long-term revenue for the short-term properties.

We start by specifying the imputation model specification we will use to estimated likely long-term (weekly) rental prices for each short-term property.

@@

We then employ a custom function to impute the long term rents for the short-term properties.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.

  imp.data <- imputeLtrRents(ltr.df=ltr.data,
                               str.df=str.data,
                               mod.spec=ltr.mod.spec,
                               match.factor='suburb')

From the imputed results, we extract the imputed rental values and merge to the original short-term data.

  # Extract out DFs (only those that imputed)
  str.metro <- merge(str.data, imp.data$imp.rent, by='property.id')

Next we impute the likely long-term search cost (days on market) for the short-term properties.

  # Apply dom to abb
  str.metro$imp.dom <- imputeDOM(str.metro, ltr.data, calc.type='median')

With the imputed DOMs and weekly rental rates we now make the an estimate of likely annual revenue if leased on the long term market. We append this to the original dataset.

  str.metro$ltr.imp.revenue <- str.metro$imp.rent * (52 - str.metro$imp.dom / 7)

Finally we make a comparison of the observed short term revenues and the imputed long term revenue and add these field back onto the original data.

  comp.revs <- compareRevenues(str.metro)

  str.metro <- merge(str.metro, comp.revs, by='property.id')

The above process of long-term revenue estimation treated the entire market as operating similarly. Realizing that the imputed long term rental values and search times may be more accurate when estimated at smaller scales, we functionalize the above processes and then apply it to short-term rentals, broken into submarkets by type, bed/bath and geographic area.  In other words, we separately estimate LTR rents for Apartments with 1bed/1bath in the city core, Apartments with 1bed/1bath in the beach submarket, etc. for all compbinations of type, bed/bath and geographic area. We then combine the results form all estimates back into a single data.frame that contains all of the short-term rentals. We use these finer scale estimates going forward (the data in the **str.data.ic** object).

@@

 str.data$tbg <- paste0(str.data$product,'.', str.data$geo.mrkt)
 ltr.data$tbg <- paste0(ltr.data$product,'.', ltr.data$geo.mrkt)

@@

  # Actual
   stra.rev <- str.data.ic[,c('property.id', 'str.act.revenue')]
   stra.rev$tenure <- 'Short-Term (Actual)   '
   names(stra.rev)[2] <- 'revenue'

  # Potential
   strp.rev <- str.data.ic[,c('property.id', 'str.pot.revenue')]
   strp.rev$tenure <- 'Short-Term (Potential)   '
   names(strp.rev)[2] <- 'revenue'

  # Long-Term
   ltr.rev <- str.data.ic[,c('property.id', 'ltr.imp.revenue')]
   ltr.rev$tenure <- 'Long-Term   '
   names(ltr.rev)[2] <- 'revenue'

  # Combine
   revdens.data <- rbind(stra.rev, strp.rev, ltr.rev)

  ## Build a plot

   rd.plot <- ggplot(revdens.data, 
                     aes(x=revenue, fill=tenure, color=tenure)) +
     geom_density(alpha=.5) +
     scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
     scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
     xlab('\nAnnual Revenue') +
     scale_x_continuous(breaks=c(seq(0, 75000, by=25000)),
                        labels=c('$0', '$25k', '$50k', '$75k'))+
     theme(legend.position='none',
           legend.title = element_blank(),
           plot.title = element_text(hjust = 0.5),
           axis.text.y = element_blank(),
           axis.ticks.y = element_blank(),
           axis.title.y=element_blank()) +
     coord_cartesian(xlim=c(0, 85000))
     rd.plot <- rd.plot + facet_wrap(~tenure)

  ## Plot

     rd.plot

@@

## Results

We will begin by analyzing the above estimates at the entire metro scale. Analyses of various submarkets will follow. Overall, we see that 31.1\% of properties raised more revenue via short term rental than expected in the long term market.

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  table(str.data.ic$str.act.pref) / nrow(str.data.ic)

@@

Next, we plot the \% of properties that have short-term preference versus the occupancy rate as occupancy rate is an important determinant of short-term preference.

@@

  str.data.ic$pref <- str.data.ic$str.act.pref

@@

   ## Make plots

  # Raw
  raw.occ.metro <- ggplot(rawocc.metro$data,
                   aes(x=x.var, y=Var))+
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none') + 
    ggtitle('Raw Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

  # Quantile
  qtl.occ.metro <- ggplot(qtlocc.metro$data,
                   aes(x=x.var, y=Var))+
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate (Pcntl)') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25th', '50th', '75th', '100th')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none') + 
    ggtitle('Percentile Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

  # Make Plot
  ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2)

@@

Next we build a heat map that shows which combinations of occupancy rate and nightly rate are most likely to result in short-term preference.

@@

  rate.hm <- abbHeatMap(str.data.ic,
                x.field='occ.rate',
                y.field='med.rate',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm + ylab('Nightly Rate')

@@

  rate.hm.svm <- abbHeatMap(str.data.ic,
                            x.field='occ.rate',
                            y.field='med.rate',
                            pref.field='str.act.pref',
                            svm=T, 
                            alpha.count=F,
                            add.points=T,
                            fill.colors=c(abb.col[1], abb.col[5]))
  rate.hm.svm+ ylab('Nightly Rate')

As the distributions of occupancy rate and nightly rate are not uniform, we standardize these values to a percentile and then replot to give a better sense of the relative level of occupancy rate and nightly rate required for short-term preference.

  qtl.hm <- abbHeatMap(str.data.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.act.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm+ ylab('Nightly  (Pcntl)')

@@

  qtl.hm.svm <- abbHeatMap(str.data.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  qtl.hm.svm+ ylab('Nightly  (Pcntl)')

@@

### Submarkets

Now we move on to looking more deeply at various submarkets.  We start by analyzing the differences between houses and apartments.

First we make a comparison table of the results.

@@

 # Make Basic comparison table
  pref.table.type <- abbCreateCompTable(ic.df=str.data.ic,
                                   split.field='type')

 # Limit to the extrapolated pref type
  pref.table.type <- pref.table.type[pref.table.type$rev.type == 'Actual', ]

@@

We then turn this into a simple chart to see the differences.

@@

  ggplot(pref.table.type, aes(x=ID, weights=Var, fill=ID)) + 
    geom_bar() +
    scale_fill_manual(values=c('red', 'blue')) +
    xlab('') +
    ylab('% of properties where Airbnb is more profitable') +
    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none')

We then look at the relationship between occ rate and preference.  Before we start though we recalculate the percentiles within each submarket.

```{r build_occ_type1, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}

 ## Create dataset

  type.data.ic <- str.data.ic

  # Id the types
  apt.id <- which(str.data.ic$type == 'Apartment')
  house.id <- which(str.data.ic$type == 'House')

  # Recalculate the percentiles
  type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id],
                                      return.type='rank')
  type.data.ic$occ.qtl[house.id] <- makeWtdQtl(
    type.data.ic$occ.rate[house.id], return.type='rank')

  type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id],
                                  return.type='rank')
  type.data.ic$rate.qtl[house.id] <- makeWtdQtl(
    type.data.ic$med.rate[house.id], return.type='rank')

Then we calculate the preference figures

```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}

 ## Calc the occ rate numbers

  rawocc.type <- abbPrefPlot(type.data.ic,
                         x.field='occ.rate',
                         split.field='type',
                         smooth=TRUE,
                         smooth.span=.5 ,
                         spl.col=c('black', 'grey40'))

  pctocc.type <- abbPrefPlot(type.data.ic,
                         x.field='occ.qtl',
                         split.field='type',
                         smooth=TRUE,
                         smooth.span=.5 ,
                         spl.col=c('black', 'grey40'))

And then plot.

```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'}

 ## Build raw plot

  ptr.occ <- ggplot(rawocc.type$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate') +
    scale_color_manual(values=c('black', 'grey60'),
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Raw Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

 ## Build Percentile Plots

  ptq.occ <- ggplot(pctocc.type$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate (Pcntl)') +
    scale_color_manual(values=c('black', 'grey60'),
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25th', '50th', '75th', '100th')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Percentile Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

 ## Plot

  ggMultiPlots(ptr.occ, ptq.occ, cols=2)

Finally, we make percentile SVM heatmaps for both apartments and houses.

```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'}

 ## Make House SVM Heatmap

  house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
                                          'House', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5])) +
  theme(legend.position='none') +
  annotate("text", x = 50, y = 50, label = "Houses", size=9) +
  ylab('Nightly Rate (Pcntl)') +
  xlab('Occupancy Rate (Pcntl)')

 ## Make Apartment SVM Heat Map

  apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type ==
                                          'Apartment', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
  annotate("text", x = 50, y = 50, label = "Apartments", size=9)+
  ylab('Nightly Rate (Pcntl)') +
  xlab('Occupancy Rate (Pcntl)')

 ## Plot

  ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2)

#### Geographic Submarkets

We now repeat the three analyses -- table, occupancy plot, heat map -- for the five geographic submarkets.

```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'}

 # Make Basic comparison table
  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                   split.field='geo.mrkt')

 # Limit to the extrapolated pref type
  pref.table <- pref.table[pref.table$rev.type == 'Actual', ]
  pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach')
  pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%')

 # Fix names  
  names(pref.table) <- c('Sub-Market', 'Short-Term Preferable')
  options(xtable.comment = FALSE)

 ## Make printable table

  print(xtable(pref.table[,1:2], 
               caption='Geographic Submarket Preferability\n',
               digits=1,
               align='llr'),
        include.rownames=FALSE,
        caption.placement='top')

```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}

 ## Build data

  subm.data.ic <- str.data.ic

  # Get IDs
  cc.id <- which(str.data.ic$geo.mrkt == 'city-core')
  city.id <- which(str.data.ic$geo.mrkt == 'city')
  sub.id <- which(str.data.ic$geo.mrkt == 'suburban')
  rural.id <- which(str.data.ic$geo.mrkt == 'rural')
  beach.id <- which(str.data.ic$geo.mrkt == 'beach')

  # Recalc the percentiles
  subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id],
                                      return.type='rank')
  subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id],
                                  return.type='rank')

  subm.data.ic$occ.qtl[city.id] <- makeWtdQtl(
      subm.data.ic$occ.rate[city.id], return.type='rank')
  subm.data.ic$rate.qtl[city.id] <- makeWtdQtl(
    subm.data.ic$med.rate[city.id], return.type='rank')

  subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id],
                                      return.type='rank')
  subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id],
                                  return.type='rank')

  subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id],
                                      return.type='rank')
  subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id],
                                  return.type='rank')

  subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id],
                                      return.type='rank')
  subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id],
                                  return.type='rank')

```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}

 ## Set colors

 ## Create plot data

  rawocc.geo <- abbPrefPlot(subm.data.ic,
                        x.field='occ.rate',
                        split.field='geo.mrkt',
                        smooth=TRUE,
                        smooth.span=.5 ,
                        spl.col=sm.col)

  pctocc.geo <- abbPrefPlot(subm.data.ic,
                         x.field='occ.qtl',
                         split.field='geo.mrkt',
                         smooth=TRUE,
                         smooth.span=.5 ,
                         spl.col=sm.col)

 ## Make plot objects

  smr.occ <- ggplot(rawocc.geo$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate') +
    scale_color_manual(values=sm.col,
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Raw Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

  smq.occ <- ggplot(pctocc.geo$data,
                    aes(x=x.var, y=Var, group=ID, color=ID)) +  
    geom_point(alpha=.5, size=.4) +
    stat_smooth(se=FALSE, size=2, span=.5) +
    xlab('\nOccupancy Rate (Pcntl)') +
    scale_color_manual(values=sm.col,
                       name='') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25th', '50th', '75th', '100th')) +
    ylab('\nSTR Preferability %') +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom') + 
    ggtitle('Percentile Rates') + 
    theme(plot.title = element_text(hjust = 0.5))

 ## Plot

  ggMultiPlots(smr.occ, smq.occ, cols=2)

```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'}

  # Build the SVM Heatmaps

  core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'city-core', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5])) +
  theme(legend.position='none') +
    ylab('') +
    xlab('') +
  annotate("text", x = 50, y = 50, label = "City-Core", size=9)

  city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'city', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "City", size=9)

  sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'suburban', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "Suburban", size=9)

  rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'rural', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "Rural", size=9)

  beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt ==
                                          'beach', ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.act.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))+
  theme(legend.position='none')+
    ylab('') +
    xlab('')+
  annotate("text", x = 50, y = 50, label = "Beach", size=9)

```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'}

  ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm,
               rural.hm.svm, beach.hm.svm, cols=2)

## Logit models

Now we attempt to explain the drivers of preference with a set of logistic regression models.

First, a basic model with just structural characteristics.

@@

  mod.act.str <- glm(str.act.pref~type+as.factor(bedbath),
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.str <- glm(str.pot.pref~type+as.factor(bedbath),
                     family=binomial(link='logit'),
                     data=str.data.ic)
```

Then a model that adds in the geographic submarkets

@@

  mod.act.loc <- glm(str.act.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.loc <- glm(str.pot.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
```

Finally a model that adds in host policies.

@@

  mod.act.host <- glm(str.act.pref~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
```

We combine all model results in to a list for easy export.

  pref.models <- list(mod.act.str, mod.act.loc, mod.act.host, 
                      mod.pot.str, mod.pot.loc, mod.pot.host)
  names(pref.models) <- c('act.str', 'act.loc', 'act.host',
                          'pot.str', 'pot.loc', 'pot.host')

@@

We then also run a set of regression models where the premium (or discount) for short-term leasing is the dependent variable.  We use the same three model specifications as above.

@@

  mod.act.str.prem <- lm(str.act.prem~type+as.factor(bedbath),
                    data=str.data.ic)
  mod.pot.str.prem <- lm(str.pot.prem~type+as.factor(bedbath),
                    data=str.data.ic)

  mod.act.loc.prem <- glm(str.act.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.loc.prem <- glm(str.pot.pref~type+as.factor(bedbath)+
                                  geo.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)

  mod.act.host.prem <- lm(str.act.prem~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
  mod.pot.host.prem <- lm(str.pot.prem~type+as.factor(bedbath)+
                        geo.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
```

We then package these into a list for easy export

    prem.models <- list(mod.act.str.prem, mod.act.loc.prem, mod.act.host.prem, 
                      mod.pot.str.prem, mod.pot.loc.prem, mod.pot.host.prem)
    names(prem.models) <- c('act.str', 'act.loc', 'act.host',
                          'pot.str', 'pot.loc', 'pot.host')

@@

## Sensitivity

### Potential Revenue

To test for the sensitivity of the result to the revenue type, we re-do some of the intial data vizs.  First we build a new preference table looking at the submarkets of type and geography.

```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}

 # Make Basic comparison table of type
  tpref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                    split.field='type')
 # Extract Potential Results
  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]

 # Make baseic comparison table of submarkets  
  spref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                    split.field='geo.mrkt')

 # Extract potential results  
  spref.table <- spref.table[spref.table$rev.type == 'Potential', ]

 # Combine and round  
  st.table <- rbind(tpref.table, spref.table)
  st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%')

 ## Fix names and print

  names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
  options(xtable.comment = FALSE)
  print(xtable(st.table[,1:2], 
               caption='Potential Revenue Preferability\n',
               digits=1, align='llr'),
               include.rownames=FALSE,
               caption.placement='top',
               hline.after=c(-1, 0, 2, 7, 7))

@@

Next we recrate the SVM percentile heat maps.

```{r pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE}

 ## create data and re-estimate the percentiles

  pot.data.ic <- str.data.ic
